\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-11-13 chapters/1_intro.tex
Small typos and changes

In Sec. \ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods for signed graphs by testing it on synthetic graphs and neuron segmentation.

>>>>

In Sec. \ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods on the task of neuron segmentation and how on synthetic graphs it achieves similar scores to a recently proposed spectral method for signed graphs.

### 2019-11-13 chapters/2_rel_work.tex
Small typos and changes

\textbf{Clustering of signed graphs} has the goal of partitioning a graph with both attractive and repulsive cues. Finding an optimally balanced partitioning has a long history in combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2019mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs. 
Another line of reseatch is given by spectral clustering methods that, on the other hand, require the user to specify the number of clusters in advance. Recently, some of these methods have been generalized to graphs with signed weights \cite{Cucuringu2019SPONGEAG,chiang2012scalable,kunegis2010spectral}, whereas others let the user specify must-link and cannot-link constraints between clusters \cite{rangapuram2012constrained,wang2014constrained,cucuringu2016simple}.

>>>>

\textbf{Clustering of signed graphs} has the goal of partitioning a graph with both attractive and repulsive cues. Finding an optimally balanced partitioning has a long history in combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
NP-hardness of the \emph{correlation clustering} problem was shown in \cite{bansal2004correlation}, while the connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problems of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy agglomerative algorithms \cite{levinkov2017comparative,wolf2019mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger graphs. 
Another line of research is given by spectral clustering methods that, on the other hand, require the user to specify the number of clusters in advance. Recently, some of these methods have been generalized to graphs with signed weights \cite{Cucuringu2019SPONGEAG,chiang2012scalable,kunegis2010spectral}, whereas others let the user specify must-link and cannot-link constraints between clusters \cite{rangapuram2012constrained,wang2014constrained,cucuringu2016simple}.

### 2019-11-13 chapters/5_experiments_cityscapes.tex
Small typos and changes

Results on the \emph{test} set are summarized in Table \ref{tab:results_cityscapes_test}. The best scores are achieved by Panoptic-DeepLab \cite{cheng2019panopticdeeplab} that proposes a more powerful CNN model to regress the centers of hte instances. The second best \emph{proposal-free} method is SSAP \cite{Gao_2019_ICCV}, which predicts long-range instance-affinities similarly to GMIS \cite{liu2018affinity}, but trains the model with extra side-losses. \algname{} with \emph{Average} linkage also achieves competitive results and outperforms the previous agglomeration method proposed in GMIS \cite{liu2018affinity}. Similarly to the experiments on neuron segmentation, results on the \emph{val} set (see Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}) show that other \algname{} linkage criteria tend to over-cluster, e.g. \emph{Abs Max}, or under-cluster and merge instances, e.g. \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and when we applied it to the affinities predicted by our fine-tuned model it achieved an AP score of 33.0 on the \emph{val} set, which is worse than the original value 34.1 reported in \cite{liu2018affinity}. This is probably due to the fact that MultiStepHAC was tailored to the output affinities of the original model. 
Table \ref{tab:extended_results_cityscapes_val} in Appendix includes the scores of all other tested \algname{} algorithms.

>>>>

Results on the \emph{test} set are summarized in Table \ref{tab:results_cityscapes_test}. The best scores are achieved by Panoptic-DeepLab \cite{cheng2019panopticdeeplab} that proposes a more powerful CNN model to regress the centers of the instances. The second best \emph{proposal-free} method is SSAP \cite{Gao_2019_ICCV}, which predicts long-range instance-affinities similarly to GMIS \cite{liu2018affinity}, but trains the model with extra side-losses. \algname{} with \emph{Average} linkage also achieves competitive results and outperforms the previous agglomeration method proposed in GMIS \cite{liu2018affinity}. Similarly to the experiments on neuron segmentation, results on the \emph{val} set (see Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}) show that other \algname{} linkage criteria tend to over-cluster, e.g. \emph{Abs Max}, or under-cluster and merge instances, e.g. \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and when we applied it to the affinities predicted by our fine-tuned model it achieved an AP score of 33.0 on the \emph{val} set, which is worse than the original value 34.1 reported in \cite{liu2018affinity}. This is probably due to the fact that MultiStepHAC was tailored to the output affinities of the original model. 
Table \ref{tab:extended_results_cityscapes_val} in Appendix includes the scores of all other tested \algname{} algorithms.

### 2019-11-13 chapters/5_experiments_spectral.tex
Update related work
Smaller plot for 8 page limit
Small typos and changes

\textbf{Synthetic graphs} - First, we generated synthetic graphs from a signed stochastic block model (SSBM) where the true number of clusters is previously known. We used an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N=10^5$ vertices and edge probability $p=0.1$. Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k=100$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) had Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $0.1$. To model noise, we flipped the sign of each edge independently with probability $\eta \in [0, 0.4]$. Median scores, 25th and 75th percentiles over 30 repetitions are shown in Fig. \ref{fig:SSBM_spectral_experiments}: GASP achieved comparable scores to the spectral methods. The specific design choice of a \emph{sign flipping} noise used in the SSBM experiments turned out to favor GASP with \emph{Sum} linkage that, according to the experiments presented in Sec. \ref{sec:results}, is the one with the lowest tendency to over-cluster and grows one cluster at the time.

@@

\begin{figure}
\centering
        \includegraphics[width=0.45\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf}
        \caption{Performances of \algname{} compared to spectral clustering methods on SSBM synthetic graphs.}
    \label{fig:SSBM_spectral_experiments}
\end{figure}
\begin{table}
\centering
\footnotesize
\begin{tabular}{l|c}
           Method & Rand-Score \\ \midrule
           \textbf{GASP Average} & \textbf{0.8966} \\
GASP Sum & 0.8965 \\
GASP Abs Max & 0.8932 \\
SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.5839\\
$L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
BNC \cite{chiang2012scalable} & 0.0074 \\
        \end{tabular}
    \caption{\algname{} compared to spectral clustering methods on a small crop of the CREMI dataset (sample B).}
    \label{tab:cremi_spectral_experiments}
\end{table}

>>>>

\textbf{Synthetic graphs} - First, we generated synthetic graphs from a signed stochastic block model (SSBM) where the true number of clusters is previously known. We used an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N=10^5$ vertices and edge probability $p=0.1$. Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k=100$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) had Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $0.1$. To model noise, we flipped the sign of each edge independently with probability $\eta \in [0, 0.4]$. Median scores, 25th and 75th percentiles over 30 repetitions are shown in Fig. \ref{fig:SSBM_spectral_experiments}: GASP achieved comparable scores to SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG}, a recently proposed spectral clustering method. The specific design choice of a \emph{sign flipping} noise used in the SSBM experiments turned out to favor GASP with \emph{Sum} linkage that, according to the experiments presented in Sec. \ref{sec:results}, is the one with the lowest tendency to over-cluster and grows one cluster at the time.

@@

\begin{figure}
\centering
        \includegraphics[width=0.4\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf} % 0.45
        \caption{Performances of \algname{} compared to spectral clustering methods on SSBM synthetic graphs. \TODO{Fix refs}}
    \label{fig:SSBM_spectral_experiments}
\end{figure}
\begin{table}
\centering
\footnotesize
\begin{tabular}{l|c}
           Method & Rand-Score \\ \midrule
           \textbf{GASP Average} & \textbf{0.8966} \\
GASP Sum & 0.8965 \\
GASP Abs Max & 0.8932 \\
SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.5839\\
$L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
BNC \cite{chiang2012scalable} & 0.0074 \\
        \end{tabular}
    \caption{\algname{} compared to spectral clustering methods on a small crop of the CREMI dataset (sample B).}
    \label{tab:cremi_spectral_experiments}
\end{table}
